A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
more centroid words

While the traditional method to measure centroids is significantly more 
challenging with \KT\ data, we have developed an alternative method
to identify centroid offsets during transits in our data.

Therefore, false positives caused by background eclipsing binaries which could
be identified as such by \kepler\ data alone will be much more difficult to
distinguish in \KT\ data, making high-contrast adaptive optics images of
planet candidates an essential follow-up tool.

>>>>

While the traditional method to measure centroids is significantly more 
challenging with \KT\ data, we have developed an alternative method
to identify centroid offsets during transits in our data.
In our data analysis, we model the systematics in the light curve
caused by spacecraft motion, constrained by the ensemble of all stars in 
the field of view.
The same can be done with the positions of each star, instead of the flux, 
as a function of time.
In this case, for each candidate, we model the time series of centroid
positions in each dimension as a linear combination of our PCA basis vectors
plus a shift of unknown amplitude during transit events.
Such a technique enables us to measure the centroid shift during transit and
quantify an uncertainty of the size of this shift.

%Therefore, false positives caused by background eclipsing binaries which could
%be identified as such by \kepler\ data alone will be much more difficult to
%distinguish in \KT\ data, making high-contrast adaptive optics images of
%planet candidates an essential follow-up tool.
